---
title: "UCSD Graduate Outcomes"
output:  html_document
params:
  dfs: NA
  dept: NA
  year: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#set working directory
#"setwd('../data_research position/data projects/first_destination/stats')

knitr::knit_hooks$set(inline=function(x){
  if(!is.numeric(x)){
    x
  } else {
    prettyNum(x, big.mark=",")
  }
})

options(scipen=999)

#load libraries
toLoad <- c("ggplot2", "plyr", "ggmap","ggthemes", "reshape2", "knitr", "kableExtra", "scales")
lapply(toLoad, library, character.only=T)

theDept <- params$dept

```

```{r echo=F,message=F}
dataframes <- params$dfs

totalgrads <- nrow(dataframes$grads)

breakdowns <- lapply(dataframes[c("employed", "continue_edu", "volunteer_service", "seeking", 
                                  "notseeking", "planto_continue_edu", "military")],
                     function(x) nrow(x[x$dept==theDept,]))
totaloutcomes <- Reduce("+", breakdowns)

bd_percents <- lapply(breakdowns, function(x) x/totaloutcomes)
bd_percents <- lapply(bd_percents, round, digits=4)
bd_percents <- lapply(bd_percents, function(x) x*100)
```

```{r echo=F}
breakdowns <- melt(breakdowns)

totalstruct <- length(dataframes$grads$Department[dataframes$grads$Department==theDept])
totalKnownStruct <- sum(breakdowns$value)
```
**Year**: `r params$year`   
**Department**: `r params$dept`  

&nbsp;

**Total UC San Diego Graduates**: `r totalgrads`
    
**Total Graduates**: `r totalstruct` (`r round(totalstruct/totalgrads, digits=4)*100`%)  
**Total Outcomes Known**: `r totalKnownStruct`  
**Department Knowledge Rate**: `r round(totalKnownStruct/totalstruct, digits = 4) * 100`%  

&nbsp;

Outcome breakdown:

```{r echo=F}
breakdowns$Outcome <- c("Employed", "Continuing Education", "Volunteering/Service", "Seeking Employment",
                "Not Seeking Employment", "Planning to Continue Education", "Military")
names(breakdowns) <- c("Count", "Outcome")
breakdowns$Percentage <- round(breakdowns$Count/totalKnownStruct, digits=4) * 100

kable_styling(kable(breakdowns,format="html"))
```

&nbsp;

```{r echo=F}
companies <- (summary(dataframes$employed$company[dataframes$employed$dept==theDept]))
companies <- companies[companies > 0]
companies <- names(companies)[-grep("^\\s*$", names(companies))]
```


**Employers**:

* `r companies[1]` 
* `r companies[2]`
* `r companies[3]`
* `r companies[4]`
* `r companies[5]`
* `r companies[6]`
* More...


&nbsp;

```{r echo=F}
structSalaries <- dataframes$employed$base_salary[dataframes$employed$dept==theDept]
```

**Salaries Reported**: `r length(structSalaries) - sum(is.na(structSalaries))` out of `r length(structSalaries)`  
**Median Salary**: $`r median(structSalaries, na.rm=T)`  
**Maximum Reported Salary**: $`r max(structSalaries, na.rm=T)`

&nbsp;

**Graduate Schools**:  

```{r echo=F}
gradSchools <- summary(dataframes$continue_edu$institution[dataframes$continue_edu$dept==theDept])
gradSchools <- gradSchools[gradSchools > 0]
gradSchools <- names(gradSchools)
```


* `r gradSchools[1]`
* `r gradSchools[2]`
* `r gradSchools[3]`
* `r gradSchools[4]`

&nbsp;
